Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-16 chi2012.tex
editted methodology section

\subsubsection{Question 1: Tasks}
All participants reported having used multiple websites to accomplish a task.  They listed example tasks such as shopping (including food, consumer electronics, hotels and flights), searching for jobs, choosing recipes, study and work.  The biggest focus for shopping focused tasks was balancing price, quality and speed of delivery.  In general, people did not not trust a single websites for reviews because they said that they could be biased and did not always review the features they were interested in.  One participant said that video reviews of items were really important because they showed the aesthetics and scale of the item.  In general for initial research into organising a task it was typical to Google keywords to find related websites to their tasks.  They identified that they used different website for different jobs, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location based decisions.  Social networks were also identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.

@@

\begin{itemize}
\item \emph{h1 -} People understand how to use DP.
\item \emph{h2 -} People can effectively mix heterogeneous data with DP.
\item \emph{h3 -} Use of DP improves or facilitates task performance
\end{itemize}

\subsubsection{Study and task design}
To test these hypotheses, we designed a within-subjects lab-based A-B study in which participants were asked to perform two of four possible predefined tasks (depending on condition), with either DP (``condition A'') or a baseline interface (``condition B'') in 2 separate timed trials.  Each participant was asked to use DP for one of the trials and the baseline interface for the other; conditions were fully counterbalanced among particiants to eliminate inadvertant ordering and task bias.

% why? why were these tasks selected? can we drop the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
The tasks were to select a restaurant for an event or university at which to study, out of six possible choices  around four possible tasks shown in Table \ref{tab:studyfactors}.

\subsubsection{Task preparation}
% how data was prepared for each of the tasks; exactly how the A condition was done (full screen DP in a web browser, no outside access to apps),  B condition and why
We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choices. The shortlist of universities and restaurants were taken from the top six ranked from the Complete University Guide (for task 1 and 2), Tripadvisor (for task 3) and Yelp (for task 4).  The top six were chosen from these websites because they provide a realistic shortlist and are comparable in terms of rankings and properties. The web sites used as data sources were chosen because they are the most popular and contain comparable statistics for universities and restaurants.

% why was the B condition set up this way? What did we seek to achieve?
The control (B) conditions were in a prepared Mac comprised of a web browser pre-loaded with a page with links to four live web sites, and an open instance of Excel with a workbook open containing spreadsheet versions of the same data as were loaded into DP for the A condition versions of the same tasks.  Other Office applications were also available for use and participants were allowed to visit other sites than the prespecified ones.  The purpose of this condition was to understand how people using standard desktop office software

\subsection{Data Collection}
Each study was overseen by a facilitator and an observer:  the role of the facilitator was to explain the study's protocol to the participant and to answer any questions; and the role of the observer was to observe without interacting with the user, and to take notes.  During the lab study, we recorded the audio and the participant's actions on screen. We asked the participants to follow a \emph{think-aloud} protocol as they worked, so that we could understand the reasoning behind their actions.  At the end of the study, the participant completed an exit survey.

% In each trials, participants were given a paper notepad and pen to use if they wished.  Screen capture software recorded all interactions with applications.  Participants were asked to follow a \emph{think-aloud} protocol as they performed each task, and audio recordings (synchronized with the screen recordings) were taken.

% This goes in results: 
% The studies lasted 40 minutes, on average.  
Both the facilitator and observer were trained on the purpose of the study, their role and how they could and couldn't influence the study.  The studies were run over 4 days.  At the end of each day the facilitators and observers met to discuss the studies' data and to revisit protocols, if necessary.

\subsection{Participant recruitement}
We recruited participants through adverts posted near the University campus and e-mails to student mailing lists.  We screened participants to be at least 18 years of age, but did not filter or preferentially select particpants based on any other criteria.  We took the first 20 that signed up and that successfully specified time slots that were available.   As described below in results, we ended up getting a large number of international students, who had varying proficiency in English.  Since all such participants had passed the requisite proficiency tests to enrol at University, we did not think this would substantially impact results.

\subsection{Task Design}

\begin{table*}[t]
\begin{center}
\small
\begin{tabular}{|p{4cm}|p{6cm}|p{6cm}|}
\hline
Task	 &Choices	&Data Sources\\
\hline
1) Three universities they would apply to study Sport Science & Universities: 1) Loughborough,  2) Durham,  3) Exeter, 4) Edinburgh, 5) Birmingham, and 6) Bath & http://www.thecompleteuniversityguide.co.uk/, http://www.ucas.ac.uk/, http://unistats.direct.gov.uk/, http://www.timeshighereducation.co.uk/world-university-rankings/ \\
\hline
2) Three universities they would apply to study History & Universities: 1) Cambridge, 2) London School of Economics and Political Science, 3) Durham, 4) Oxford, 5) St Andrews, and 6) University College London & http://www.thecompleteuniversityguide.co.uk/, http://www.ucas.ac.uk/, http://unistats.direct.gov.uk/, http://www.timeshighereducation.co.uk/world-university-rankings/ \\
\hline
3) Restaurant they would book for 12 friends in Cambridge&Restaurants : 1) Alimentum, 2) Gardenia Restaurant, 3) The Cambridge Chop House, 4) Al Casbah, 5) Midsummer House Restaurant, and 6) Nando's Restaurant. & www.yelp.co.uk, www.tripadvisor.co.uk, http://ratings.food.gov.uk/, facebook and google plus.\\
\hline
4) Restaurant they would book for 12 friends in Glagow & Restaurants :1) Black Sheep Bistro, 2) Charcoals, 3) Number 16 Family Restaurant, 4) Fanny Trollopes Cafe, 5) Two Fat Ladies At The Buttery, and 6) Sapori D'Italia. & www.yelp.co.uk, www.tripadvisor.co.uk, http://ratings.food.gov.uk/, facebook and google plus.\\
\hline
\end{tabular}
\end{center}
\caption{Tasks, choices and data sources} \label{tab:studyfactors}
\normalsize
\end{table*}%

Each task had an A and B condition.  The A condition, the participant could only use DataPalette to make their decision; and in the B condition the participant was given the choice to using any websites they desired and or workbook in Microsoft Excel containing the data taken from the data sources to make their choice on individual spreadsheets.

Each study consisted of two tasks, one A and one B condition.  Each participant was given 10 minutes to complete a task.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

@@

We recruited 20 participants (10 female) from the University of Southampton's international student mailing list.  All of the participants spoke English, and for 12 of them, English was not their first language.  Predominately the participants were studying various levels of Computer Science, and 5 of which studied other subjects.

>>>>

\subsubsection{Question 1: Tasks}
All participants reported having used multiple websites to accomplish a task.  They listed example tasks such as shopping (including food, consumer electronics, hotels and flights), choosing restaurants, searching for jobs, when choosing a university, choosing recipes, study and work.  The biggest focus for shopping focused tasks was balancing price, quality and speed of delivery.  In general, people did not not trust a single websites for reviews because they said that they could be biased and did not always review the features they were interested in.  One participant said that video reviews of items were really important because they showed the aesthetics and scale of the item.  In general for initial research into organising a task it was typical to Google keywords to find related websites to their tasks.  They identified that they used different website for different jobs, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location based decisions.  Social networks were also identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.

@@

\begin{itemize}
\item \emph{h1 -} People understand how to use DP.
\item \emph{h2 -} People can effectively mix heterogeneous data with DP.
\item \emph{h3 -} Use of DP improves or facilitates task performance.
\end{itemize}

\subsubsection{Study and task design}
To test these hypotheses, we designed a within-subjects lab-based A-B study in which participants were asked to perform two predefined tasks in separate timed trials.  The participants asked to use either our DP (``condition A'') or a baseline interface (``condition B'') to complete a task, and we used two possible dataset for each type of task.  We used an A and B condition so that we could compare how users performed their tasks using our interface and the standard approach.  We also used two datasets for each of the tasks, so that we evaluate whether the participant's performance of completing a task differed with different datasets.  Each participant was asked to use DP for one of the trials and the baseline interface for the other; conditions were fully counterbalanced among participants to eliminate inadvertent ordering and task bias.

% why? why were these tasks selected? can we drop the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on these scenarios on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people choose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two courses for the university task at random from a list taken form the complete university guide\footnote{}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choicesex

\subsubsection{Task preparation}
% how data was prepared for each of the tasks; exactly how the A condition was done (full screen DP in a web browser, no outside access to apps),  B condition and why
In order to prepare the data for our tasks, we identified websites that people commonly used for selecting universities and restaurants.  Once we had compiled the list of websites, we select the top most used six for each task.  We selected six because it enable us to scope our study, we found through two pilot studies that six data sources provided a sufficient challenge for users to explore the data and required them to use DP's main features.  We manually collected the data from the nine selected websites into jason files, and converted them to Microsoft Excel worksheets (which 40\% of the participants in PS.1 said that they used to compare data in).

% why was the B condition set up this way? What did we seek to achieve?
The control (B) conditions were in a prepared Mac comprised of a web browser pre-loaded with a page with links to four live web sites, and an open instance of Excel with a workbook open containing spreadsheet versions of the same data as were loaded into DP for the A condition versions of the same tasks.  Other Office applications were also available for use and participants were allowed to visit other sites than the pre-specified ones.  The purpose of this condition was to understand how people using standard desktop office software.

\subsection{Data Collection}
Each study was overseen by a facilitator and an observer:  the role of the facilitator was to explain the study's protocol to the participant and to answer any questions; and the role of the observer was to observe without interacting with the user, and to take notes.  Both the facilitator and observer were trained on the purpose of the study, their role and how they could and couldn't influence the study.   Explicitly both the facilitator and observer where trained in identifying processes that people used during a task, so that they could thematically categorise them.  Initially, we identified the following themes: organisation of data, eliminating candidates, co-referencing, and visualisations. The studies were run over 4 days.  At the end of each day the facilitators and observers met to discuss the studies' data and to revisit protocols, if necessary.  During the lab study, we recorded the audio and the participant's actions on screen. We asked the participants to follow a \emph{think-aloud} protocol as they worked, so that we could understand the reasoning behind their actions.  At the end of the study, the participant completed an exit survey.

\subsection{Participant Recruitement}
We recruited participants through adverts posted near the University campus and e-mails to student mailing lists.  We screened participants to be at least 18 years of age, but did not filter or preferentially select participants based on any other criteria.  We took the first 20 that signed up and that successfully specified time slots that were available.   As described below in results, we ended up getting a large number of international students, who had varying proficiency in English.  Since all such participants had passed the requisite proficiency tests to enrol at University, we did not think this would substantially impact results.

\subsection{Experimental Setup}

The participants were given a standard desktop PC running MacOS X on a 22" monitor with a standard keyboard and mouse.  During the studies the Excel workbook and DP were initially set to full screen by default.  Each participant was asked to complete two tasks, one A and one B condition.  Each participant was given 10 minutes to complete a task.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

%Each task had an A and B condition.  The A condition, the participant could only use DataPalette to make their decision; and in the B condition the participant was given the choice to using any websites they desired and or workbook in Microsoft Excel containing the data taken from the data sources to make their choice on individual spreadsheets.

%Each study consisted of two tasks, one A and one B condition.  Each participant was given 10 minutes to complete a task.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

%\begin{table*}[t]
%\begin{center}
%\small
%\begin{tabular}{|p{4cm}|p{6cm}|p{6cm}|}
%\hline
%Task	 &Choices	&Data Sources\\
%\hline
%1) Three universities they would apply to study Sport Science & Universities: 1) Loughborough,  2) Durham,  3) Exeter, 4) Edinburgh, 5) Birmingham, and 6) Bath & http://www.thecompleteuniversityguide.co.uk/, http://www.ucas.ac.uk/, http://unistats.direct.gov.uk/, http://www.timeshighereducation.co.uk/world-university-rankings/ \\
%\hline
%2) Three universities they would apply to study History & Universities: 1) Cambridge, 2) London School of Economics and Political Science, 3) Durham, 4) Oxford, 5) St Andrews, and 6) University College London & http://www.thecompleteuniversityguide.co.uk/, http://www.ucas.ac.uk/, http://unistats.direct.gov.uk/, http://www.timeshighereducation.co.uk/world-university-rankings/ \\
%\hline
%3) Restaurant they would book for 12 friends in Cambridge&Restaurants : 1) Alimentum, 2) Gardenia Restaurant, 3) The Cambridge Chop House, 4) Al Casbah, 5) Midsummer House Restaurant, and 6) Nando's Restaurant. & www.yelp.co.uk, www.tripadvisor.co.uk, http://ratings.food.gov.uk/, facebook and google plus.\\
%\hline
%4) Restaurant they would book for 12 friends in Glagow & Restaurants :1) Black Sheep Bistro, 2) Charcoals, 3) Number 16 Family Restaurant, 4) Fanny Trollopes Cafe, 5) Two Fat Ladies At The Buttery, and 6) Sapori D'Italia. & www.yelp.co.uk, www.tripadvisor.co.uk, http://ratings.food.gov.uk/, facebook and google plus.\\
%\hline
%\end{tabular}
%\end{center}
%\caption{Tasks, choices and data sources} \label{tab:studyfactors}
%\normalsize
%\end{table*}%

@@

We recruited 20 participants (10 female) from the University of Southampton's international student mailing list.  All of the participants spoke English, and for 12 of them, English was not their first language.  Predominately the participants were studying various levels of Computer Science, and 5 of which studied other subjects.   On average each study took 40 mins to complete the tasks and exit surveys.
